\documentclass[10pt]{extarticle}
\usepackage{styles/packages}
\usepackage{styles/style}

\begin{document}
	
	\init

	\begin{sidebar}{images/logo.pdf}{darthpoezd@gmail.com}

		\hfill
		{
			\iconsfont\fontsize{20}{18}\selectfont
			\href{https://t.me/AriosJentu}{T}
			\href{https://github.com/AriosJentu}{G}
			\href{https://AriosJentu.artstation.com/}{A}
			\href{https://drive.google.com/drive/folders/1hcmudyfBtrOo7_3qARUckmqdiUvxr0jT?usp=drive_link}{D}
		}

		\titletxt{Skills}

		\toptxt{Hard-Skills}

		\deftxt{
			\begin{itemize}[label=\icirc]
				\itemindent=-15pt
				\item \textbf{3D-Modeling} -- Blender \vp
				\item \textbf{Rendering} -- Cycles, Eevee \vp
				\item \textbf{Animation} -- Blender \vp
				\item \textbf{Texturing} -- Krita, GIMP, Blender \vp
				\item \textbf{Level-design} -- NetRadiant \vp
				\item \textbf{Vector graphics} -- Inkscape \vp
				\item \textbf{Voxel graphics} -- MagicaVoxel \vp
				\item Drawing skills on graphics tablet \vp
			\end{itemize}
		}

		\toptxt{Soft-Skills}

		\deftxt{
			\begin{itemize}[label=\icirc]
				\itemindent=-15pt
				\item Communication \vp
				\item Adaptability \vp
				\item Creativity \vp
				\item Teamwork \vp
				\item Work ethic \vp
				\item Attention to detail \vp
			\end{itemize}
		}

		\toptxt{Languages}

		\deftxt{
			\begin{itemize}[label=\icirc]
				\itemindent=-15pt
				\item \textbf{Russian} -- Native \vp
				\item \textbf{English} -- B2 \vp
				\begin{itemize}[label=]
					\itemindent=-35pt
					\item EF SET Quick Check -- 86/100
					\item EF SET -- 56/100
				\end{itemize}
			\end{itemize}
		}

	\end{sidebar}

	\begin{centralpart}{Pavel Maksimov}{P}{}
		\begin{titleblock}{About}{}{}{}
			I'm 25 y.o. 3D artist, and I have a passion for creating 3D visuals and animations, as well as helping other to understand the power of 3D design. Extensive experience in education and training of students in the field of mathematics in modeling.
		\end{titleblock}

		\begin{titleblock}{3D-Environment artist}{}{}{}
			3D environment artist with over 5 years of experience designing objects, weapons and structures for visualization tasks and game development purposes. Worked on level design for some games such as Quake/Xonotic for over 3 years. I have a desire to study level design in game development and environmental modeling.
		\end{titleblock}
	\end{centralpart}

	\setlength{\currentpos}{\getposy+5pt}
	
	\begin{centralpart}{Work Experience}{J}{}
		\begin{titleblock}{University teacher}{2019-Current}{Far Eastern Federal University}{}
			\begin{itemize}[label=$\circ$]
				\item Developed my own course on Computer Graphics, the main task of which is to develop a simple visualization engine based on analytical geometry.
				\item I have been teaching a course on differential methods for 4 years. A lot of teaching methodologies and software solutions have been developed in this area.
			\end{itemize}
		\end{titleblock}
		\begin{additionalblock}{Achievements}
			Certificates of contribution to the development of the educational processes and scientific activities.
		\end{additionalblock}
		\begin{titleblock}{3D-Environment artist}{2018-2021}{4A IT Khabarovsk}{\href{https://4ait.ru/}{Link (clickable)}}
			\begin{itemize}[label=$\circ$]
				\item Was the main 3D artist in the Design team.
				\item Developed concepts for enterprise equipment and environment for visualization purposes.
			\end{itemize}
		\end{titleblock}
		\begin{additionalblock}{Achievements}
			Ensured customer satisfaction with 3D visualizations of their solutions at every stage of product development.
		\end{additionalblock}
	\end{centralpart}

	\setlength{\currentpos}{\getposy+5pt}
	
	\begin{centralpart}{Education}{E}{}
		\begin{titleblock}{Far Eastern Federal University}{2016-2020}{Bachelor of Applied Mathematics and Informatics}{}
		\end{titleblock}
		\begin{titleblock}{Far Eastern Federal University}{2020-2022}{Master of Applied Mathematics and Informatics}{}
			Specialization: Numerical analysis and modeling of physical processes.
		\end{titleblock}
	\end{centralpart}

	\setlength{\currentpos}{\getposy+5pt}
	\begin{centralpart}{Links}{L}{t}
		\begin{titleblock}{}{}{}{}
			\vspace*{-25pt}
			\begin{itemize}[label=$\circ$]
				\item Telegram: {\color{sidetopsep}\href{https://t.me/AriosJentu}{https://t.me/AriosJentu}} \vp
				\item GitHub: {\color{sidetopsep}\href{https://github.com/AriosJentu}{https://github.com/AriosJentu}} \vp
				\item ArtStation: {\color{sidetopsep}\href{https://AriosJentu.artstation.com/}{https://ariosjentu.artstation.com}} \vp
				\item Portfolio: {\color{sidetopsep}\href{https://drive.google.com/drive/folders/1hcmudyfBtrOo7_3qARUckmqdiUvxr0jT?usp=drive_link}{Link (clickable)}} \vp
			\end{itemize}
		\end{titleblock}
	\end{centralpart}

	\setlength{\currentpos}{\getposy+20pt}
	% \begin{centralpart}{}{}{t}
	% 	\begin{titleblock}{Wishes}{}{}{}
	% 		\vspace*{-8pt}
	% 		\begin{itemize}[label=$\circ$]
	% 			\item Relocation
	% 			\item Payment in crypto
	% 		\end{itemize}
	% 	\end{titleblock}
	% \end{centralpart}

	\signature{S}
	\bottomtext{This document was designed in XeLaTeX: \color{sidetopsep}\href{https://github.com/AriosJentu/Resume}{GitHub}}

\end{document}

#ищуработу
3D-дизайнер окружения/3D-моделлер

Софт:
— Blender
— Krita, GIMP
— Inkscape
— MagicaVoxel

Навыки Hard:
— Моделирование
— Текстурирование
— Анимирование

Навыки Soft:
— Коммуницирование
— Адаптивность
— Креативность
— Командная работа
— Преподавание

Опыт:
— 2 года коммерческого моделирования
— 8 лет моделирования как хобби в Blender
— 3 года level-design для игр Quake/Xonotic

Контакты:
— Telegram: @AriosJentu
— E-Mail: darthpoezd@gmail.com